\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}
\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[unicode, draft=false]{hyperref}
\usepackage{fontawesome5}

% Centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

% Section formatting
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

% Hyperref color setup
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% Job entry environments
\newenvironment{jobshort}[2]{
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
}{}

\newenvironment{joblong}[2]{
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
}{
    \end{itemize}
    \end{minipage}
}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{}C@{}}
\Huge{Thân Vĩnh Huy} \\[7.5pt]
\href{https://github.com/k4sp3rz}{\raisebox{-0.05\height}\faGithub\ k4sp3rz} \ $|$ \
\href{https://www.linkedin.com/in/vĩnh-huy-thân-a2b06a36a}{\raisebox{-0.05\height}\faLinkedin\ Thân Vĩnh Huy} \ $|$ \
\href{mailto:k4sp3rofficial@gmail.com}{\raisebox{-0.05\height}\faEnvelope\ k4sp3rofficial@gmail.com} \ $|$ \
\href{tel:+84907803197}{\raisebox{-0.05\height}\faMobile\ +84.907.803.197} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Enthusiastic undergraduate student with hands-on experience building web and mobile applications across the stack. Comfortable working with C\#, ASP.NET MVC, Entity Framework, SQL Server, JavaScript, Bootstrap, Flutter, and Dart. Able to create responsive user interfaces, develop RESTful APIs, connect applications to databases, and manage basic project workflows. Dedicated to writing clean, maintainable code and contributing effectively in team settings. Eager to learn new technologies and ready to apply my skills as an intern in a real-world software development environment.

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{EcommerceClothShop} & \hfill \href{https://github.com/k4sp3rz/EcommerceClothShop}{GitHub Link} \\[3.75pt]
\end{tabularx}
\vspace{-0.5em}
\begin{itemize}[leftmargin=1.5em]
    \item Full-featured e-commerce web application built with ASP.NET MVC and Entity Framework.
    \item Includes user authentication, product catalog, shopping cart, order management, and admin dashboard.
    \item Integrated basic payment functionality and role-based access control.
\end{itemize}

\vspace{1em}
\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Huoo Music App} & \hfill \href{https://github.com/FoxeiZ/huoo}{GitHub Link} \\[3.75pt]
\end{tabularx}
\vspace{-0.5em}
\begin{itemize}[leftmargin=1.5em]
    \item Contributed to the development of a cross-platform music streaming app using Flutter and Dart.
    \item Implemented features including audio playback, user-friendly UI, and performance optimizations.
    \item Collaborated with team members using Git and followed clean code practices.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2022 - Present & \textbf{Ho Chi Minh City University of Foreign Languages – Information Technology}, Bachelor of Software Engineering \hfill (GPA: 2.83/4.0) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming Languages & C\#, Dart, JavaScript, HTML/CSS \\
Frameworks & ASP.NET MVC, Flutter, Bootstrap \\
Tools & Git, GitHub, Visual Studio, VS Code, SQL Server Management Studio \\
Databases & Microsoft SQL Server, SQLite \\
Soft Skills & Teamwork, Problem-solving, Self-learning, Time management \\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
